Meta RL analyses

### 2018-10-15 meta_RL_analyses.Rmd

```{r}
num_runs = 3
results_dir = "results/results_smd/"
```

@@

reward_d = reward_d %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str))
```

>>>>

```{r}
num_runs = 3
results_dir = "results/results_smd/"

new_game_strs = c("game_straight_flush_l_1_bv_1_sr_0")
```

@@

reward_d = reward_d %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = game_str %in% new_game_strs)
```

```{r}
avg_reward_d = reward_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

```{r}
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
```

```{r}
ggplot(avg_reward_d, aes(x=game_type, fill=is_new_game, y=avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2")
```
